Insert the article title here

### 2020-07-21 tex/ClementiBarba2020.tex
add path to figs and pack to avoid errors
fix errors with bibstyle

@@

\begin{fmtext}   %I DON'T GET WHAT WE ARE SUPPOSE TO PUT HERE, BUT THE GUIDELINES HAVE THIS
\section{Intro}

PUT SOMETHING HERE

@@

\maketitle
I dont know why all the text goes in warning

>>>>

\graphicspath{{figs/}} %  PATH to figure files-- change to ./ for submission

@@

\begin{fmtext}  
\section{fist page thing}

PUT SOMETHING HERE. I DON'T GET WHAT WE ARE SUPPOSE TO PUT HERE, BUT THE GUIDELINES HAVE THIS

@@

\maketitle
% Body of paper.

\section{Results} \label{sec:results}
\input{results}

\bibliographystyle{vancouver}
\bibliography{pygbe_rep_val} %don't leave spaces between elements, it throws error
